Analysis of Physical Activity Survey(2022)

### 2022-04-27 outputs/paper/paper.Rmd
Finished Model

  In section \@ref(Data) we talk about the process of gathering and analyzing the dataset and the variables. Then in section \@ref(Results) we discuss the implications of the dataset presented. Finally in section \@ref(Discussion) we discuss implications for the United States citizens, as well as the weakness of the study and the further investigation that may be useful to the topic of recreational activity support and physical activity in the United States.

@@

  Figure \@ref(fig:fig5) shows the relationship between 150min of Aerobics training and Muscle Training compared to the rate of Obesity.

@@

@@

  From Figure \@ref(fig:fig1) we see a chart comparing the proportion of respondents who were obese based on the different states in the country. We can see from the chart that all states lie between a rate of 20% and 35% obese. The chart below is for 2011

@@

>>>>

  In section \@ref(Data) we talk about the process of gathering and analyzing the dataset and the variables. Then in the \@ref(Model) section we build a linear model for the rate of obesity. Then in section \@ref(Results) we discuss the implications of the dataset presented. Finally in section \@ref(Discussion) we discuss implications for the United States citizens, as well as the weakness of the study and the further investigation that may be useful to the topic of recreational activity support and physical activity in the United States.

@@

  Both Muscle Training and 150min of Aerobic Training had significant p-values in this model of 0.0236 and 0.0027 respectively. Below Figure \@ref(fig:fig5) shows the relationship between 150min of Aerobics training and Muscle Training compared to the rate of Obesity. There was strong positive correlation to people with 300min of aerobic training, and those who did muscle training or 150min of aerobic training so including that interaction was not beneficial. Additionally those that do no aerobic training at all are strongly negatively correlated with those that do 150min or more. Soi including that interaction was not beneficial to the model.

  Our data does not have any particularly large outliers that would disturb the model present. And our outcome variable, the proportion of residents who are obese is a continuous variable, thus the bilinear model seems the best choice.

@@

And below Figure \@ref(fig:fig6) shows us the relationship between the rate of obesity and the proportion of a states residents participating in muscle training excercises.

```{r fig6, echo = FALSE, fig.cap = "Obesity vs Muscle Training", fig.width=5,fig.height=5}
ggplot(mapping = aes(x = Muscle, y = Obesity))+geom_point()+xlab("Muscle") +
  ylab("Obesity Rate")
```

@@

  From Figure \@ref(fig:fig1) we see a chart comparing the proportion of respondents who were obese based on the different states in the country. We can see from the chart that all states lie between a rate of 20% and 35% obese. The chart below is for 2011.

@@

   Using our model from the
